\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-25 eg6-letters/NIM/EG6_RTPC_NIM.tex
update figures 2, 6, and 10 in the nim paper

\begin{figure}[tb]
\centering
\includegraphics[scale=0.28]{fig/RTPC_1_all.png}
\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to 
the beam direction.  See text for description of the elements.} 
\label{fig:RTPC_1_4}
\end{figure}

@@

Triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
is received by a FEC-board, a programmable number of samples $N_0$ is digitized 
and stored in a data memory, and hence processed by the digital circuit. Upon 
arrival of Level-2 trigger, the latest processed samples are saved in a 
multi-event memory, invididual to each-channel, ready for readout by the RCU. 
In our setup, the RCU receives the trigger signal from the CLAS Trigger 
Supervisor system, and distributes both L1 and L2 signals to all the FECs in 
the crate, with a definite L1-L2 trigger latency. Such latency is programmable, 
and has to be longh enough to accomodate the digitization of the $N_0$ samples 
per channel. In the current implementation, $N_0=100$ samples/channel are 
acquired for each trigger, operating ALTRO at the reduced sampling frequency 
of $10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.

The trigger signal also initiates RCU readout operation from FEC boards. All 
the measured samples from active channels are reported, together with a channel 
identifier and a timestamp, to the ROC application, that in turns sends them on 
the main event builder. During data reconstruction, the acquired samples are 
processed to obtain, for each readout pad, the accumulated charge (ADC) and 
the pulse time (T). Since pulse time was obtained as the time-stamp of the 
first sample above threshold, referred to to the trigger time, the resolution 
is equivalent to the ALTRO sampling time, 100~ns.

@@

In order to reduce the data size, ALTRO is operated in zero-suppression mode: 
only samples above a programmable threshold are stored in the ALTRO on-board 
memory and then written to tape. A glitch-filter permits to reject spurious 
pulses due to noise, by requiring the presence of a minimum number of samples 
over threshold $N_{MINSEQ}$ to validate a sample. To properly reconstruct 
the signal shape, $N_{PRE}$ samples before threshold-crossing and $N_{POST}$ 
samles after the signal returns below threshold are saved. In the present 
configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set 
just above the noise level.

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/RTPC_2.png}
\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
near 35 mm longitudinal position along the RTPC. The black line represents 
the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_all.pdf}
\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to the beam 
direction.  See text for description of the elements.} \label{fig:RTPC_1_4}
\end{figure}

@@

Triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
is received by a FEC-board, a programmable number of samples $N_0$ is digitized 
and stored in a data memory, and hence processed by the digital circuit. Upon 
arrival of Level-2 trigger, the latest processed samples are saved in a 
multi-event memory, individual to each-channel, ready for readout by the RCU.  
In our setup, the RCU receives the trigger signal from the CLAS Trigger 
Supervisor system, and distributes both L1 and L2 signals to all the FECs in 
the crate, with a definite L1-L2 trigger latency. Such latency is programmable, 
and has to be long enough to accommodate the digitization of the $N_0$ samples 
per channel.  In the current implementation, $N_0=100$ samples/channel are 
acquired for each trigger, operating ALTRO at the reduced sampling frequency of 
$10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.

The trigger signal also initiates RCU readout operation from FEC boards. All 
the measured samples from active channels are reported, together with a channel 
identifier and a time-stamp, to the ROC application, that in turns sends them 
on the main event builder. During data reconstruction, the acquired samples are 
processed to obtain, for each readout pad, the accumulated charge (ADC) and the 
pulse time (T). Since pulse time was obtained as the time-stamp of the first 
sample above threshold, referred to to the trigger time, the resolution is 
equivalent to the ALTRO sampling time, 100~ns.

@@

In order to reduce the data size, ALTRO is operated in zero-suppression mode: 
only samples above a programmable threshold are stored in the ALTRO on-board 
memory and then written to tape. A glitch-filter permits to reject spurious 
pulses due to noise, by requiring the presence of a minimum number of samples 
over threshold $N_{MINSEQ}$ to validate a sample. To properly reconstruct 
the signal shape, $N_{PRE}$ samples before threshold-crossing and $N_{POST}$ 
samples after the signal returns below threshold are saved. In the present 
configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set just 
above the noise level.

@@

\begin{figure}[tb]
\centering
%\includegraphics[scale=0.4][trim={0 5cm 0 0},clip]{fig_2017/RTPC_1_4.pdf}
\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_4.pdf}
\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{fig_2017/FitResult_p2_11.pdf}
\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
near 35 mm longitudinal position along the RTPC. The black line represents 
the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}
